Fivebranes

### 2022-03-01 fivebranes/fivebranes.tex
fivebrane

\section{The $J$'s}

@@

>>>>

\section{The $E(3,6)$ symmetry}

@@

\subsection{Embedding $E(3|6)$ into twisted supergravity}

\parsec[]
First we explain how $E(3|6)$ embeds inside of $E(5|10)$. 
We follow \cite{KacCheng}.

A vector field $X = X(z) \in \Vect(\C^3)$ embeds as the vector field
\[
X \mapsto X(z) - \frac12 (\del X)(z) \sum_{i=1}^2 w_a \del_{w_a} .
\]
Here, $\del X$ is the divergence of $X$ with respect to the standard holomorphic volume form on $\C^3$. 
The elements $e,h,f \otimes f(z) \in \lie{sl}(2) \otimes \C[z_i]$ embed as the vector fields
\[
f(z) w_1 \del_{w_2} , \quad f(z) (w_1 \del_{w_2} - w_2 \del_{w_1}, \quad f(z) w_2 \del_{w_1} . 
\]
respectively.

Next, we explain how the odd summand embeds. 
Recall, a general element in the odd part of $E(3|6)$ can be written as
\[
g(z) \del_{z_i}^{1/2} \otimes r_\pm .
\]
This element embeds into $E(5|10)$ as the following closed two-form
\[
\del \left((w_1-w_2) g(z) \d z_i \right) .
\]
\brian{check this}

\subsection{The local Lie algebra}

Let $\cE(5|10)$ be the following local Lie algebra on $X \times \C^2 \times \R$.

Let $\pi \colon X \times \C^2 \times \RR \to X$. 
We will give a model $\cG_{grav}$ for $\pi_* \cE(5|10)$ as a local Lie algebra on $\C^3$.

First, introduce the holomorphic line bundle 
\[
w_1^k w_2^\ell \cO_{X} \define ??  .
\]
Let $\lie{s}_2$ denote the Lie algebra of polynomial vector fields in the variables $w_1,w_2$ which preserve the holomorphic volume form $\d w_1 \d w_2$.

\begin{dfn}
Let $\cG_{grav}$ be the following local Lie algebra on the complex three-fold $X$. 
\begin{itemize}
\item The even part is 
\[
\Omega^{0,\bu}(X , \T_X \otimes \cO_X [w_1,w_2]) \oplus \Omega^{0,\bu}(X , \lie{s}_2) .
\]
\item The odd part is 
\[
\Omega^{\geq 2, \bu}(X, \cO_X[w_1,w_2]) \oplus \Omega^{1,\bu}(X, w_1 \cO_X[w_1,w_2]) \oplus \Omega^{1,\bu}(X, w_2 \cO_X[w_1,w_2]) \oplus \cdots
\]
\end{itemize} 
\end{dfn}

\parsec

Consider the following auxiliary grading on the local Lie algebra $\cG_{grav}$. 
The variables $w_a$ are declared to have weight $+1$. 
%The variables $\til w_a$ are declared to have weight $-1$. 
Additionally, parity has weight $-1$.
Thus, for example, the weight of $w_1 \d z_1 \d z_2$ is zero.
